Ladies' figure skating in the 2002 Winter Olympics

### 2025-12-12 inst/skating.Rmd
typo
cite Lock and Lock

---
title: "Ladies' figure skating in the 2002 Winter Olympics"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib
---

@@

To cite the `hyper2` package in publications, please use
@hankin2017_rmd.  This document analyses Bradley-Terry strengths of
the competitors in the Ladies' Figure Skating at the 2002 Winter
Olympics.  In the package, dataframe `skating_table` is copied from
Lock and Lock (see skating.Rd for more details).  It also creates file
`data/skating.rda` which contains R objects `skating`,
`skating_table`, and `skating_maxp`.

@@

Object `skating_table` is an order table.  It is structured so that
each competitor is a row, and each judge is a column.  One good thing
to do is to present the dataset as an order table;

>>>>

---
title: "Ladies' figure skating in the 2002 Winter Olympics"
author: "R. K. S. Hankin"
output: bookdown::html_document2
link-citations: true
bibliography: hyper2.bib
---

@@

To cite the `hyper2` package in publications, please use
@hankin2017_rmd.  This document analyses Bradley-Terry strengths of
the competitors in the Ladies' Figure Skating at the 2002 Winter
Olympics.  In the package, dataframe `skating_table` is copied from
Lock and Lock -@lock2003.  It also creates file `data/skating.rda`
which contains R objects `skating`, `skating_table`, and
`skating_maxp`.

@@

Object `skating_table` is an _order table_.  It is structured so that
each competitor is a row, and each judge is a column.  One good thing
to do is to present the dataset as a _rank table_:
